Toward nonlinear multigrid \\ for nonlinear variational inequalities

### 2023-02-05 talk/slides.tex
a bit more about VIs

\begin{frame}{general VI problems}

\begin{itemize}
\item let $\mathcal{K}$ be a closed and convex subset of a Banach space $\mathcal{V}$
\item suppose $F:\mathcal{K} \to \mathcal{V}'$ is a continuous, generally nonlinear \emph{operator}
    \begin{itemize}
    \item[$\circ$] $F$ may be defined only on $\mathcal{K}$
    \end{itemize}
\item the general problem VI($F$,$\mathcal{K}$) is
	$$\ip{F(u)}{v-u} \ge 0 \text{ for all } v \in \mathcal{K}$$

\bigskip
\item analogy:

\begin{tabular}{l|l}
x & y \\ \hline
z & w
\end{tabular}
\end{itemize}
\end{frame}

>>>>

\begin{frame}{general variational inequalities}

\begin{itemize}
\item let $\mathcal{K}$ be a closed and convex subset of a Banach space $\mathcal{V}$
\item suppose $F:\mathcal{K} \to \mathcal{V}'$ is a continuous, generally nonlinear \emph{operator}
    \begin{itemize}
    \item[$\circ$] $F$ may be defined only on $\mathcal{K}$
    \item[$\circ$] $F$ may \emph{not} be the derivative of a $J(u)$
    \end{itemize}
\item the general problem {\color{FireBrick} VI($F$,$\mathcal{K}$)} is
	$${\color{FireBrick} \ip{F(u)}{v-u} \ge 0 \quad \text{ for all } v \in \mathcal{K}}$$
\end{itemize}
\end{frame}

\begin{frame}{VI $=$ ``constrained equation''}

\begin{center}
\begin{tabular}{l|l}
\begin{minipage}[t][16mm][t]{0.4\textwidth}
unconstrained optimization:
$$\min_{u\in\mathcal{V}} J(u)$$
\end{minipage}
&
\begin{minipage}[t][16mm][t]{0.4\textwidth}
constrained optimization:
$$\min_{u\in\mathcal{K}} J(u)$$
\end{minipage}
\\ \hline
\begin{minipage}[t][16mm][t]{0.4\textwidth}
solve equation for $u \in \mathcal{V}$: {\LARGE \strut}

$$F(u)=0$$
\end{minipage}
&
\begin{minipage}[t][16mm][t]{0.4\textwidth}

\vspace{-2mm}
solve {\color{FireBrick} VI($F$,$\mathcal{K}$)} for $u \in \mathcal{K}$:
$${\color{FireBrick} \ip{F(u)}{v-u} \ge 0 \quad \forall v \in \mathcal{K}}$$
\end{minipage}
\end{tabular}
\end{center}
\end{frame}

\begin{frame}{most familiar case}

\begin{itemize}
\item we even teach VIs when we introduce calculus

\includegraphics[width=\textwidth]{images/calcone.png}
\end{itemize}
\end{frame}
